---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hedgeroot

<!-- badges: start -->
[![License](https://img.shields.io/badge/License-AGPL--3-blue.svg)](LICENSE)
[![R-CMD-check](https://github.com/sims1253/hedgeroot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sims1253/hedgeroot/actions/workflows/R-CMD-check.yaml)
[![Tests](https://github.com/sims1253/hedgeroot/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/sims1253/hedgeroot/actions/workflows/test-coverage.yaml)
[![Codecov test coverage](https://codecov.io/gh/sims1253/hedgeroot/graph/badge.svg)](https://app.codecov.io/gh/sims1253/hedgeroot)
[![GH-Pages](https://github.com/sims1253/hedgeroot/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/sims1253/hedgeroot/actions/workflows/pkgdown.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

HedgeRoot is the data management foundation for the Hedgerow trading system. It provides a robust, production-ready data infrastructure package that handles high-performance data fetching, validation, storage, and management capabilities for financial data.

## Key Features

- **Multi-Source Data Integration**: Support for Alpha Vantage, Interactive Brokers, and Yahoo Finance
- **Advanced Provider Management**: Intelligent failover with circuit breakers and health monitoring
- **High-Performance Architecture**: Leverages data.table for optimal performance
- **Comprehensive Data Validation**: Built-in quality control and anomaly detection
- **S7 Object System**: Modern, type-safe data structures

## Installation

You can install the development version of hedgeroot from GitHub:

```r
# Install devtools if you haven't already
install.packages("devtools")

# Install hedgeroot
devtools::install_github("sims1253/hedgeroot")
```

## Basic Usage

### Simple Data Provider

```{r example, eval = FALSE}
library(hedgeroot)

# Create a provider
provider <- create_alpha_vantage_provider(api_key = "your_api_key")

# Fetch OHLCV data
data <- fetch_ohlcv(provider, "AAPL", "2023-01-01", "2023-12-31")
```

### Advanced Provider Management

```{r advanced-example, eval = FALSE}
# Create multiple providers with failover
providers <- list(
  create_alpha_vantage_provider(api_key = "your_av_key"),
  create_ib_provider(host = "127.0.0.1", port = 7497)
)

# Create advanced manager with circuit breaker
manager <- create_advanced_provider_manager(
  providers = providers,
  failover_strategy = "priority",
  circuit_breaker_threshold = 3,
  circuit_breaker_window = 15
)

# Fetch data with automatic failover
data <- fetch_ohlcv(manager, "AAPL", "2023-01-01", "2023-12-31")
```

### Data Validation

```{r validation-example, eval = FALSE}
# Validate fetched data
validation <- validate_data(data)

# Check validation results
if (validation@is_valid) {
  cat("Data quality score:", validation@quality_score, "\n")
} else {
  cat("Validation errors:", validation@errors, "\n")
}
```

## Architecture

### Provider System

HedgeRoot uses a modular provider system supporting:

- **Alpha Vantage**: Free and paid tiers for equity and forex data
- **Interactive Brokers**: Professional trading platform integration  
- **Yahoo Finance**: Free equity data through quantmod
- **Custom Providers**: Extensible architecture for new data sources

### Failover Strategy

- **Priority-based**: Providers tried in order of priority
- **Health-based**: Providers selected based on historical performance
- **Circuit Breaker**: Failing providers temporarily disabled
- **Automatic Recovery**: Providers re-enabled after cooldown period

## Configuration

### Environment Variables

```bash
# Alpha Vantage API key
export ALPHA_VANTAGE_API_KEY="your_api_key"

# IB Gateway settings
export IB_HOST="127.0.0.1"
export IB_PORT="7497"
export IB_CLIENT_ID="1"
```

## Contributing

1. Fork the repository
2. Create a feature branch
3. Make your changes with tests
4. Ensure all tests pass with `devtools::check()`
5. Submit a pull request

## License

This project is licensed under the AGPL-3 License. See the LICENSE file for details.